---
title: "PSY 8960 Week 8 Project"
author: "Nga Do"
date: "`r Sys.Date()`"
output: html_document
    
---

<style>
h4.date {
  font-style: italic;
}
</style>

# Reproducible Image and Online Resources

An image of this project as of date can be accessed by [clicking this link]().
An interactive web app is available by [clicking this link]() instead.

# Script Settings and Resources
```{r echo=TRUE, warning=FALSE,message=FALSE, error=FALSE}
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
library(tidyverse)
```

# Data Import and Cleaning
Import data, convert time data to standard format, convert variables to factor format and reverse code q5, filter q6 to remove cases failed manipulation check.
```{r}
week8_tbl <-  read.csv(file = "../data/week3.csv") |>
  mutate(timeStart = ymd_hms(timeStart),
         timeEnd = ymd_hms(timeStart),
         gender = factor(gender, levels=c("M","F"),
                         labels = c("Male","Female")),
         condition=factor(condition, levels=c("A", "B", "C"),
                           labels=c("Block A", "Block B", "Control")),
         q5= 6 - q5) |> 
  dplyr::filter(q6 == 1)
```

# Visualization
Mutate to create two variables for mean q1-q6 and mean q8-q10 and create a scatter plot of the relationship between mean score q1-q6 and mean score q8-q10
```{r echo=FALSE,message=FALSE}
week8_tbl %>% select(q1:q6)
(week8_tbl <-  week8_tbl %>% 
  mutate(mean_q1_q6 = rowMeans(select(., q1:q6)),
         mean_q8_q10 = rowMeans(select(., q8:q10)))) %>% 
  ggplot(aes(x=mean_q1_q6, y=mean_q8_q10)) + 
  geom_jitter() + 
  geom_smooth(method = "lm", color = "purple") +
  labs(x="Mean q1-q6",
       y="Mean q8-q10",
       title = "Scatterplot of mean q1-q6 and mean q8-q10")
```

# Analysis
Correlation between mean score of q1-q6 and mean score of q8-q10 is `r cor.test(week8_tbl$mean_q1_q6, week8_tbl$mean_q8_q10)[["estimate"]][["cor"]]`. p > .05 so the relationship between the two mean scores are not significantly different from 0.

```{r echo=FALSE}
cor.test(week8_tbl$mean_q1_q6, week8_tbl$mean_q8_q10)
```

# Data Export
Export data for shiny, only keep necessary variables
```{r}
shiny_tbl <- week8_tbl %>% 
  select(timeEnd, gender, mean_q1_q6, mean_q8_q10) %>% 
  saveRDS("../shiny/shiny.rds")
```

```{r}
# Render to out folder
rmarkdown::render("week8.Rmd", output_file = "../out/week8.html")
```

